### 2024-07-11 analysis/analysis.qmd
updated analysis heterogenuity issues

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp <- dplyr::filter(R_studies,dimension=="valence")
dim(tmp)
tmp <- tmp[!is.na(tmp$values),]
dim(tmp)

@@

m.cor <- metacor(cor = values,     # values 
                 n = stimulus_n,
                 studlab = unique_id, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

@@

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp <- dplyr::filter(R_studies,dimension=="arousal")
dim(tmp)
tmp <- tmp[!is.na(tmp$values),]
dim(tmp)
#tmp<-drop_na(tmp)

m.cor <- metacor(cor = values, 
                 n = stimulus_n,
                 studlab = unique_id,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

>>>>

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="valence")
#tmp <- dplyr::filter(R_studies,dimension=="valence")
#dim(tmp)

#if all studies, remove two
#tmp <- tmp[!is.na(tmp$values),]
#dim(tmp)

@@

m.cor <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")

@@

# select regression studies with r2
tmp <- dplyr::filter(R_summary,dimension=="arousal")
#tmp <- dplyr::filter(R_studies,dimension=="arousal")
dim(tmp)
#tmp <- tmp[!is.na(tmp$values),]
dim(tmp)
#tmp<-drop_na(tmp)

m.cor <- metacor(cor = valuesMax, 
                 n = stimulus_n,
                 studlab = citekey,
                 data = tmp,
                 fixed = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 backtransf = TRUE,
                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Arousal: Summary")

### 2024-07-11 analysis/preprocessing.qmd
updated analysis heterogenuity issues

## Pull data to analyse regression studies

@@

```
### Homogenise the outcome variable names to valence and arousal

@@

### Diagnostics

@@

### Select a summary measure for valence and arousal separately

@@

### Visualise Summary on two dimensions

@@

### Plot success across the years

@@

g3 <- ggplot(R_studies,aes(x=year,y=values,colour=model_class_id))+
  geom_point(show.legend = T)+
  facet_wrap(.~dimension)+
  theme_bw()
g3
```
### Simple model complexity metric

@@

### Explore feature_n_complexity and model success

@@

### Create descriptive table for the manuscript

@@

### Export as csv

@@

## Pull data to analyse classification studies

@@

```
### Homogenise the outcome variable names to valence and arousal

@@

@@

g3 <- ggplot(R_studies,aes(x=year,y=values,colour=model_class_id))+
  geom_point(show.legend = T)+
  facet_wrap(.~dimension)+
  theme_bw()
g3
```
### Simple model complexity metric

@@

### Export as csv

>>>>

# Pull data to analyse regression studies

@@

## Homogenise the outcome variable names to valence and arousal

@@

## Diagnostics

@@

## Select a summary measure for valence and arousal separately

@@

## Visualise Summary on two dimensions

@@

## Plot success across the years

@@

g3 <- ggplot(R_studies,aes(x=year,y=values,colour=model_class_id))+
  geom_point(show.legend = T)+
  facet_wrap(.~dimension)+
  theme_bw()
g3
```

## Simple model complexity metric

@@

## Explore feature_n_complexity and model success

@@

## Create descriptive table for the manuscript

@@

## Export as csv

@@

# Pull data to analyse classification studies

@@

```
## Homogenise the outcome variable names to valence and arousal

@@

g1<-ggplot(C_studies,aes(x=values,fill=citekey,color=dimension))+
  geom_histogram()+
  facet_wrap(.~model_class_id)+
  scale_color_manual(values = c('black','white'))+
  theme_dark()+
  scale_x_continuous(breaks = seq(0,1,by=.1))

@@

g3 <- ggplot(R_studies,aes(x=year,y=values,colour=model_class_id))+
  geom_point(show.legend = T)+
  facet_wrap(.~dimension)+
  theme_bw()
g3
```
## Simple model complexity metric

@@

## Export as csv

```{r}
#write.csv(x = R_studies,file = 'R_studies.csv')
#write.csv(x = R_summary,file = 'R_summary.csv')
```

### 2024-07-11 manuscript/manuscript.qmd
updated analysis heterogenuity issues

| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
| Valence All | 49,42480  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% |
| Val. MaxTrim|   8,7205  | 0.6140 [0.5538; 0.6679] | 18.5|.0001 | 0.008| 88.5% |
| *N Features*|           |                         |     |      |      |       |
| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| *Techniques*|           |                         |     |      |      |       |
|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

@@

| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
| Arousal     | 55,43160   | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
| Arousal Trim| 27,18402   | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
| Arousal M   | 14,10641   | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
| Arousal Md  | 14,10641   | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
| Arousal Max | 14,10641   | 0.8077 [0.7088; 0.8755] | 10.3|0.0001|0.155 | 96.8%  |
| Aro.Max.Trm | 11,10021   | 0.7869 [0.7490; 0.8197] | 25.6|0.0001|0.0132| 96.8%  |

>>>>

| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$| Prediction interval
|:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
| Valence All | 49,42480  | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
| Valence Trim| 27,18402  | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
| Valence M   | 14,10641  | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
| Valence Md  | 14,10641  | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
| Valence Max | 14,10641  | 0.6520 [0.5026; 0.7636] | 7.44|.0001 | 0.142| 97.9% | -0.0719; 0.9260
| Val. MaxTrim|   8,7205  | 0.6140 [0.5538; 0.6679] | 18.5|.0001 | 0.008| 88.5% | 0.4470; 0.7396
| *N Features*|           |                         |     |      |      |       |
| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| *Techniques*|           |                         |     |      |      |       |
|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

OTHER GROUPINGS? STIMULUS MIXED/SINGLE GENRE, PREDICTION/EXPLANATION,

see this to ignore I^2 and rely on prediction interval: 
https://onlinelibrary.wiley.com/doi/full/10.1002/jrsm.1678

@@

| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
| Arousal     | 55,43160   | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
| Arousal Trim| 27,18402   | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
| Arousal M   | 14,10641   | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
| Arousal Md  | 14,10641   | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
| Arousal Max | 14,10641   | 0.8077 [0.7088; 0.8755] | 10.3|0.0001|0.155 | 96.8%  | 0.2258; 0.9648
| Aro.Max.Trm | 11,10021   | 0.7869 [0.7490; 0.8197] | 25.6|0.0001|0.0132| 96.8%  | 0.6372; 0.9047
